\section{Introduction}
\noindent
	For 4 months from August 2017 until December 2017, I did an Internship at Codyssey Web
Nepal, an outsourcing software and web application development company which has an
expertise in Web Development and Solution Engineering. The company has a very good and
healthy environment, where I got abundant possibilities and chances to sharpen my skill and
extend my knowledge further in the field of web development.
\newline

\noindent
During my Internship, I worked on Leaves Management System, which is basically an
application which allows employees to request leaves to their team managers, where the
manager can view leaves and accept/reject leaves. The application is a tier application, where
it has two different dimensions. One being the backend logic or the server, which is
developed using the popular web framework Ruby on Rails and the other being the frontend
or the client, developed using another popular UI library ReactJs, which is a JavaScript
library.
\newline

\noindent
The scope of the project is determined to be applicable for any company and an organization,
since every organization or company has employees and every employee are in need of
leaves sooner or later. This project can also applicable for researchers as a reference for
building a system similar to mentioned afore. This project is limited to leaves management
and not HRM.

\section{Background}
Prior to digging deep into the report, one has to have a basic understanding about a web
application and how they work.
\newline
\noindent
