\section{Literature Review}
\subsection{TimeOffManager}
\noindent
TimeoffManager.com offers numerous important features, ranging from ease-of-use and simplicity to scalability. Its ease-of-use makes it easy for anyone to use it, while its scalability lets companies of every sizes have the peace of mind to know that all their employees’ time-off requests are being managed efficiently.

\subsection{Plan My Leave}
\noindent
PlanMyLeave.com is an easy to use and secure online leave management system that calculates
accurate leave balances in real time. It offers visibility into leave entitlements and gives a
clear picture of resource availability to managers. It is Feature rich, automatic and easy to
use. It is a leave management system with powerful functionality and settings that make it
very easy to set up and automate absence management.

\subsubsection{Key Features}
1. Approval Escalation and auto approve \newline
2. HR Information System \newline
3. Access, usage and mobility \newline
4. Leave approval workflow \newline
5. Apply leave for others and View past leave approvals \newline
6. Editing submitted / approved leave requests \newline
7. Auto approvals and Notifications \newline

\subsection{adp.in}
The ideal leave management tool to support the workforce trends of the present and future.
Align your leave policies with ADP Vista HCMSM and protect your organization from gambits that result in lost productivity. Automate leave grants, get consolidated reports and improve overall employee compliance with your leave policies.

\subsubsection{Key Features}
1. Online Leave Transactions \newline
2. Easy Report Generation \newline
3. Workflow Notification \newline
4. Customizable Leave Policies